\section{Gutenberg-Richter Least Squares} - Coded (Not implemented)

The least squares is the simplest approach for fitting an a- and b-value for an unbounded Gutenberg \& Richter (1944) model. Generally no longer used due to bias from large magnitudes.

\section{Maximum Likelihood (Aki 1965, Bender 1983)} - Currently Available

The classical maximum likelihood estimator for a simple unbounded Gutenberg \& Richter (1985) model is that of Aki (1965), adapted for binned magnitude data by Bender (1983). Assumes a fixed $M_C$ value for the catalogue (assumes a simple power law recurrence model) and does not explicitly take into account magnitude uncertainty. We adjust for this by taking the catalogue with time-varying completeness and divide it into S sub-catalogues, where each sub-catalogue corresponds to a period with a corresponding $M_C$. An “average” a- and b-value (with uncertainty) is returned by taking the mean of the a- and b-value of each sub-catalogue, weighted by the number of events in each sub-catalogue.

\begin{equation}
   \hat{b} = \frac{1}{S} \sum_{i = 1}^{S} w_i b_i
\end{equation}

An alternative estimator, proposed by Kijko \& Smit (2012) utilises the weighted harmonic mean of the estimators from each subcatalogue:

\begin{equation}
   \tilde{\beta} = \left( {\sum_{i = 1}^{S} \frac{w_i}{\beta_i} } \right) ^{-1}
\end{equation}

where $\beta = b \ln \left( {10} \right)$ and $w_i =n_i / n$. Then for the catalogue composed of S subcatalogues, each of $t_i$ years, the rate of earthquakes greater than or equal to a given magnitunde $m_{min}$ ($\lambda \left( {m_{min}} \right) $) is given as:

\begin{equation}
   \lambda \left( {m_{min}} \right) = \frac{n}{\sum_{i = 1}^{S} t_i \exp \left[ {-\beta \left( {m_{min}^i - m{min}} \right) } \right]}
\end{equation}

%\section{Optimisation (e.g. ZMAP)}
%
%This approach is the ZMAP adaptation of the MLE estimator, taking into account temporal variation in completeness, which is not dissimilar to the previously described methodology. Here, for each sub-catalogue, the log-likelihood that the distribution corresponds to a Poisson distribution is determined, and the total negative log-likelihood of the fit of the model to the whole catalogue taken by summing the likelihoods. A gradient-descent optimisation is applied to minimise the negative log-likelihood for the whole catalogue. Appears to only return the best estimate of a- and b-value (not the uncertainties), and does not take into account magnitude uncertainty.

\section{\cite{weichert1980}}

\begin{equation}
   b = \frac{ \log_{10} \left( e \right)}{ \bar{m} - m_0 + \left( {\frac{\Delta M}{2}} \right)}
\end{equation}

Recognising the typical conditions of an earthquake catalogue, \cite{weichert1980} developed an algorithm to determine an unbiased estimate of $b$ for grouped magnitudes and unequal periods of observation. The likelihood formulation for this approach is:

\begin{equation}
   \mathbf{L} \left( {\beta | n_i, m_i, t_i} \right) = \frac{ N!}{\prod_i n_i!} \prod_i p_{i}^{n_i}
\end{equation}

where $\mathbf{L}$ is the likelihood estimator of $\beta$, $n$ the number of earthquakes in magnitude bin m with observation period t. The parameter $p$ is defined as:

\begin{equation}
   p_i = \frac{t_i \exp \left( {-\beta m_i} \right) }{\sum_j t_j \exp \left( {-\beta m_j} \right)}
\end{equation}

The extremum of $\ln \left( {\mathbf{L}}\right)$ is found at:

\begin{equation} 
   \frac{\sum_i t_i m_i \exp \left( {-\beta m_i} \right)}{\sum_j t_j \exp \left( {-\beta m_j} \right)}
\end{equation}

The computational implementation of this method is given as an appendix to \cite{weichert1980}. This formulation of the maximum likelihood estimator for b-value, and consequently seismicity rate, is in widespread use, with applications in many national seismic hazard analysis \citep[e.g.]{usgsNSHM1996,usgsNSHM2002}. The algorithm has been demonstrated to be efficient and unbiased for most applications. It is recognised by \citet{Felzer2008} that an implicit assumption is made regarding the stationarity of the seismicity for all the time periods. 


%\section{Kijko \& Sellevol (1989)}
%
%\section{Penalised MLE (Johnston, 1994; CEUS, 2012)} – Reviewing code
%
%\section{Tapered Gutenberg \& Richter (Kagan, 2002)} – Preliminary matlab code (cannot account for error!)
%
%\section{Generalised MLE (e.g. Utsu, 1999)}

%\section{Extreme Value Statistics (i.e. Epstein \& Lomnitz, Gumbel Types I/III)}