In this chapter we discuss the properties of the two main calculators 
needed to process the information contained in the \gls{pshainputmodel} 
and prepare it for calculation: the Logic Tree processor and the 
Earthquake Rupture Forecast calculator. 

In Section \ref{hazard:logic_tree_processor} we describe the logic 
tree processor which takes the PSHA Input Model and creates many 
realisations of a \gls{seismicsourcemodel} and of a 
\gls{groundmotionmodel} while in the following two Sections we concentrate 
on the Earthquake Rupture Forecast Calculator which takes one seismic
sources model - produced by the Logic Tree Processor - and creates 
the \gls{acr:erf}.  
%
% ------------------------------------------------------------------------------
\section{The Logic Tree Processor}
\label{hazard:logic_tree_processor}
\index{Logic Tree!Processor}
%
The Logic Tree Processor is responsible for processing data in a 
PSHA input model describing the two logic tree structures
(see Section \ref{hazard:logic_tree}). 
%
The processing consists on the creation of a \gls{seismicsourcemodel} 
from the seismic source logic tree (see Section 
\ref{hazard:source_model_logic_tree}) and one \gls{groundmotionmodel} 
from the ground-motion logic tree (see Section \ref{hazard:gmpe_logic_tree}). 
%
%The seismic source model and ground-motion model created can be then 
%passed to the different OpenQuake-Hazard calculators: the classical PSHA 
%calculator (described 
%in Section \ref{chap:classic_psha}) and the stochastic PSHA calculator 
%(discussed in Section \ref{chap:stochastic_psha}).

The potential difficulty in processing the information in a logic tree 
is constrained by its size, the complexity of the structure and the 
intricacy of the \glspl{branchset} involved.
%
For a large logic tree, performing a seismic hazard calculation for 
all possible end-branch models is an unfeasible task, therefore, 
an approach based on Monte Carlo sampling appears a more efficient and
thus feasible approach. 
%
On the contrary, for a small and simple logic tree, a Monte Carlo 
approach is inefficient with respect to enumerating all the possible 
end-branch models and performing a hazard analysis for each of them. 
%
In other words, to get stable results in case of a simple logic tree, 
a Monte Carlo approach would require sampling epistemic uncertainties 
a number of times much larger than the actual number of end-branch models.
%
The general plan for OpenQuake is to provide both the two processing 
strategies. 

Currently, the logic tree processor can only provide a Monte 
Carlo sampler.
%
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{The Logic Tree Monte Carlo Sampler}
Aim of the \gls{acr:ltmcs} is to create a set of \glspl{seismicsourcemodel} 
and \glspl{groundmotionmodel} representing exhaustively the combinations 
allowed by the logic tree structures defined by the modeller.
% 
This way the distribution of the final results will reflect 
the degree of uncertainty introduced by lack of precise knowledge 
of parameters and models included in the PSHA input model.
%
%. . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . .
\subsubsection{Sampling the seismic source logic tree}
As described in \ref{hazard:source_model_logic_tree}, the first branching 
level in the source model logic tree is used to define one or more 
alternative source models called \glspl{initialseismicsourcemodel}. 
%
Subsequent branches define parameter-specific epistemic uncertainties. 
\textcolor{red}{Currently} each branching level contains only one 
branch set (therefore producing a symmetric logic tree). 

The \gls{acr:ltmcs} constructs a \gls{seismicsourcemodel} by progressively
processing all the branching levels. In the first branching level, an 
\gls{initialseismicsourcemodel} is randomly selected, with a probability 
equal to the uncertainty 
weight. 
%
Epistemic uncertainties defined in subsequent branching levels are then 
applied to this initially selected source model. For each following 
branching level, a loop over the seismic sources defined in the selected
source model is started, and for each seismic source an epistemic 
uncertainty value is randomly selected (again with a probability equal to 
the uncertainty weight).
%
\subsubsection{Sampling the ground-motion logic tree}
The ground-motion logic tree allows the definition of multiple branch sets 
(containing different ground-motion models), each referring to a specific 
tectonic region type. 
%
The sampling of the ground-motion logic tree takes place by looping 
over the different tectonic region types defined by the modeler, and, for 
each of them, by randomly selecting a GMPE according to its weight. 
%
The final set of samples will contain therefore a ground-motion model for
each tectonic region type considered in the source model.
%
For both the source model and ground-motion logic trees, the sampling
of the epistemic weights is performed by using the inverse transform method (\citet{martinez2002}).
The method consists in computing the inverse distribution function of the epistemic weights,
and then generating a uniform random number between 0 and 1, that put as argument of the inverse transform function, gives a epistemic uncertainty model with a probability equal to the
associated weight.
